D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-16 ootavacuous.tex
Add roadmap for "A Definition of Semantic Dependency"
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@@ Roadmap

>>>>

Section~\ref{sec:For Compilers Using Single-Thread Analysis}
focuses on compilers that restrict their analysis to a single
thread,
Section~\ref{sec:For Compilers Using Global Analysis}
slightly relaxes this single-thread restriction,
Section~\ref{sec:Verifying the Fundamental Property}
verifies the fundamantal property of semantic dependencies,
and
Section~\ref{sec:Outstanding Issues}
discusses a general questions regarding our definitions.
